Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-06-07 paper/letter.tex
new paragraph on the multiphase model

However, the physical interpretation of Ly-$\alpha$ observations is
not straightforward. 
This is due to the resonant nature of the Ly-$\alpha$ line. 
A Ly-$\alpha$ photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are very few analytically tools available to interpret the
Ly-$\alpha$ line.
They are applicable only in very few cases of highly symmetrical
conditions, which are hardly met in real astrophysical systems.

For these reasons the interpretation of Ly-$\alpha$ observations
require state-of-the-art Monte Carlo radiative transfer simulations.   
Recent advances in these computational models
\cite{GaravitoCamargo2014} have shown that galaxy rotation imprints an
effect on the Lyman-$\alpha$ line.
The most important consequence of rotation is that even for a
spherical gas distribution, the line morphology now depends on the
viewing angle respect to the rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity
and the line center and the line width increase with rotational
velocity. 
When the rotational velocity is close to the half-line width of the
static line the line becomes single peaked, as it is observed in
\tol, a unique feature that other theoretical models find
difficult to reproduce without invoking complex gas distributions.

@@

>>>>

However, the physical interpretation of Ly-$\alpha$ observations is
not straightforward. 
This is due to the resonant nature of the Ly-$\alpha$ line. 
A Ly-$\alpha$ photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are very few analytically tools available to interpret the
Ly-$\alpha$ line.
They are applicable only in very few cases of highly symmetrical
conditions, which are hardly met in real astrophysical systems.
For these reasons the interpretation of Ly-$\alpha$ observations
require state-of-the-art Monte Carlo radiative transfer simulations.   
Recent advances in these computational models have explored the
effects that bulk rotation and a multiphase state in the interstellar
medium should have on on the Lyman-$\alpha$ line.

The most important consequence of bulk rotation is that, even for a
spherical gas distribution, the line morphology now depends on the
viewing angle respect to the rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity
and the line center and the line width increase with rotational
velocity. 
When the rotational velocity is close to the half-line width of the
static line the line becomes single peaked, as it is observed in
\tol, a unique feature that other theoretical models find
difficult to reproduce without invoking complex gas distributions.

In the case of a multiphase interstellar medium there are a wide variety
of possible emerging spectra, mostly due to the increased complexity
of a model that must take into account the behaviour of neutral hydrogen
clumps dispersed in a tenous intraclump medium. 
This variety includes single, double and triple peaked
spectra. 
A clumpy interstellar medium also facilitates the escape of Ly
continuum and \lya\ photons.

@@

FIXME: Add non detection in 2MASS %\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
